\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
internal representation

\subsection*{A.P.I.}
In our model, algorithmic policies interact with packets through A.P.I function calls before returning a forwarding decision. We include in Figure~\ref{fig:range_api} the core of our \lstinline|A.P.I.|. 
\lstinline|field| enumerates the different fields of a packet. It can be extended to represent more fields of a packet's header. Associated with \lstinline|field| are \lstinline|range|s, possible values taken by a certain packet's field, within a given minimum value \lstinline|min_value| and maximum value \lstinline|max_value|. \lstinline|range| consists of list of integer pairs, representing a collection of intervals whose union correspond to the range of values of a packet. For simplicity, we consider integer fields here, but this could be extended, for example, to IP prefix, boolean flags, etc.

@@

@@

\subsection*{Tracing the Algorithmic Policy}
From an algorithmic policy, we generate a decision tree  whose leaves are forwarding decision and whose node are either branching according the range of a field value, according to a relation ,or adding and removing components from a relation.

>>>>

\subsection*{A.P.I.}
In our model, algorithmic policies interact with packets through A.P.I function calls before returning a forwarding decision. We include in Figure~\ref{fig:range_api} the core of our \lstinline|A.P.I.|.

@@

\lstinline|field| enumerates the different fields of a packet. It can be extended to represent more fields of a packet's header. Associated with \lstinline|field| are \lstinline|range|s, possible values taken by a certain packet's field, within a given minimum value \lstinline|min_value| and maximum value \lstinline|max_value|. \lstinline|range| consists of list of integer pairs, representing a collection of intervals whose union correspond to the range of values of a packet. For simplicity, we consider integer fields here, but this could be extended, for example, to IP prefix, boolean flags, etc.

@@

The rest of the API, included in Figure~\ref{fig:build_api}, consists of functions used to interact with Red Oak. \lstinline|compile| is used to trace a policy from a given function from packet to forwarding \lstinline|decision|. \lstinline|run| simulates the compiled \lstinline|policy| on a series of \lstinline|examples|. In the remainder of this section, we describe these functions in more detail.

\subsection*{Internal Representation of Packets and Policies}

Packet are represented abstractly in the API as type \lstinline|pkt|, and are treated as concrete packet by algorithmic policies. In contrast, internally, \lstinline|pkt| represents a class of packet which could reach a certain point in the program. We call this class of packet a symbolic packet.
A symbolic packet consists of two parts:
\begin{itemize}
\item a map from \lstinline|field| to \lstinline|range|, representing the range of possible value from the class of packet
  \item a list of pairs of \lstinline|relation| and list of \lstinline|field| representing the relation that the relevant \lstinline|field|'s value of the symbolic packet should be in. 
  \end{itemize}

A \lstinline|policy| is represented internally as a decision tree whose leaves are forwarding decision and whose node are either branching according the range of a field value, according to a relation, or adding and removing components from a relation. To simplify rule generation, we also record in the tree the most general symbolic packet who can reach leaves, \lstinline|Add| and \lstinline|Remove| nodes.

\subsection*{Tracing the Algorithmic Policy}
From an algorithmic policy, we generate a decision tree using the function \lstinline|compile|.
